### 2016-02-19 docs/ms_communitySynchrony.Rmd
updates citations in intro

Introduction
------------
The relationship between species richness and ecosystem stability depends on species synchrony [@Gonzalez2009].
All else being equal, the stability of ecosystem function is highest when species dynamics are asynchronous [@DeMazancourt2013a].
Thus, a mechanistic understanding of the diversity-stability relationship requires understanding the processes that increase or decrease species synchrony in nature.
In the simplest case, when interspecific interactions and demographic stochasticity are weak, species synchrony is entirely determined by the synchrony of species' responses to fluctuating environmental conditions [@Loreau2008a; @Loreau2013].
Synchrony is highest when correlations among species' environmental responses are perfectly postive, intermediate when species' environmental responses are independent, and lowest when the correlations of species' environmental responses are perfectly negative [@Ives2002; @Loreau2008a; @Loreau2013].
Of course, real communities are subject to many internal and external forces beyond environmental fluctuations that can affect synchrony and complicate predictions from special theoretical cases [@Loreau2013].

@@

g1 <- ggplot()+
  geom_line(data=subset(synch_df, type=="IPM"), aes(x=value, color=Var2), 
            stat="density", adjust=2)+
  geom_vline(data=obs_pgr_df, aes(xintercept=pgr_synch, color=Var2), linetype=2)+
  facet_wrap("Var2", ncol=1, scales="free_y")+
  scale_color_manual(values = c("grey45", "steelblue", "slateblue4", "darkorange", "purple"))+
  guides(color=FALSE)+
  xlab("Community Synchrony")+
  ylab("Estimated Probability Density")+
  ggtitle("IPM")+
  theme_bw()

g2 <- ggplot()+
  geom_line(data=subset(synch_df, type=="IBM"), aes(x=value, color=Var2), 
            stat="density", adjust=2)+
  geom_vline(data=obs_pgr_df, aes(xintercept=pgr_synch, color=Var2), linetype=2)+
  facet_wrap("Var2", ncol=1, scales="free_y")+
  scale_color_manual(values = c("grey45", "steelblue", "slateblue4", "darkorange", "purple"))+
  guides(color=FALSE)+
  xlab("Community Synchrony")+
  ylab("Estimated Probability Density")+
  ggtitle("IBM")+
  theme_bw()

>>>>

Introduction
------------
The relationship between species richness and ecosystem stability in grasslands depends on species synchrony [@Tilman2006; @Isbell2009; @Hector2010; @Hautier2014].
All else being equal, the stability of ecosystem function is highest when species dynamics are asynchronous [@DeMazancourt2013a].
Thus, a mechanistic understanding of the diversity-stability relationship requires understanding the processes that increase or decrease species synchrony in nature.
In the simplest case, when interspecific interactions and demographic stochasticity are weak, species synchrony is entirely determined by the synchrony of species' responses to fluctuating environmental conditions [@Loreau2008a; @Loreau2013].
Synchrony is highest when correlations among species' environmental responses are perfectly postive, intermediate when species' environmental responses are independent, and lowest when the correlations of species' environmental responses are perfectly negative [@Ives2002; @Loreau2008a; @Loreau2013].
Of course, real communities are subject to many internal and external forces beyond environmental fluctuations that can affect synchrony and complicate predictions from special theoretical cases [@Loreau2013].

@@

g1 <- ggplot()+
  geom_line(data=subset(synch_df, type=="IPM"), aes(x=value, color=Var2), 
            stat="density", adjust=2)+
  geom_vline(data=obs_pgr_df, aes(xintercept=pgr_synch, color=Var2), linetype=2)+
  facet_wrap("Var2", ncol=1, scales="free_y")+
  scale_color_manual(values = c("grey45", "steelblue", "slateblue4", "darkorange", "purple"))+
  guides(color=FALSE)+
  xlab("Community Synchrony")+
  ylab("Estimated Probability Density")+
  ggtitle("IPM")+
  scale_x_continuous(limits=c(0,1))+
  theme_bw()

g2 <- ggplot()+
  geom_line(data=subset(synch_df, type=="IBM"), aes(x=value, color=Var2), 
            stat="density", adjust=2)+
  geom_vline(data=obs_pgr_df, aes(xintercept=pgr_synch, color=Var2), linetype=2)+
  facet_wrap("Var2", ncol=1, scales="free_y")+
  scale_color_manual(values = c("grey45", "steelblue", "slateblue4", "darkorange", "purple"))+
  guides(color=FALSE)+
  xlab("Community Synchrony")+
  ylab("Estimated Probability Density")+
  ggtitle("IBM")+
  scale_x_continuous(limits=c(0,1))+
  theme_bw()
